How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-10 brainscopycut.tex
thx-jp

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE\\Friedrichstr. 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Telmo Menezes, Jean-Pierre Nadal, Sharon Peperkamp, and Nicolas Baumard for useful suggestions and comments.

>>>>

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Telmo Menezes, Jean-Philippe Cointet, Jean-Pierre Nadal, Sharon Peperkamp, and Nicolas Baumard for useful suggestions and comments.
